MSstatsPTM: Statistical relative quantification of post-translational modifications in bottom-up mass spectrometry-based proteomics

### 2022-07-12 main/MSstatsPTM_Main.tex
minor fig caption changes

\begin{figure}[ht]
\centering
\begin{subfigure}[c]{0.5\linewidth}
\includegraphics[width=1\textwidth]{images/ipah_venn_diagramm.png}
\caption{}
\label{fig:data4_venn_diagram}
\end{subfigure}
\begin{subfigure}[c]{0.5\linewidth}
\includegraphics[width=1\textwidth]{images/shig_venn_diagramm.png}
\caption{}
\label{fig:data5_venn_diagram}
\end{subfigure}
\caption{a) Dataset 4: Human - Ubiquitination - 1mix-TMT. The overlap of differential modified peptides for the PTM model with and without global protein level adjustment across all comparisons.  3,236 modified peptides became insignificant, 1,352 became significant, while 4,282 were significant in both models. b) Dataset 5: Mouse - Phosphorylation - 2mix-TMT. a) The overlap of differentially modified peptides between the PTM model with and without global protein level adjustment across all comparisons. 19,286 peptides became insignificant, 4,947 became significant, and 41,552 were significant in both models. }
\label{fig:venn_diagrams}
\end{figure}

\begin{figure}[h!]
\centering
\begin{subfigure}{\textwidth}
 \centering
\includegraphics[width=1.0\textwidth]{images/No_Difference_Shigella_Profile_Plot}
\caption{}
\label{fig:data4_profile_plot}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=1.0\textwidth]{images/IpaH_prof_plot.png}
	\caption{}
	\label{fig:data5_profile_plot}
	 \end{subfigure}
\caption{a) Dataset 5: Mouse - Phosphorylation - 2mix-TMT. Comparing the global profiling of protein $TTP$ with the modification of the protein at site $S178$. When looking at the summary of the modification and global protein it was clear the difference between conditions followed the same trend. Specifically, there was a positive adjustment in abundance when comparing WT\_Uninfect to WT\_Late in both the modification and global profiling run. This indicated the movement was driven by changes in global protein that was only accounted for in the model after adjusting for global protein abundance change. b) Dataset 4: Human - Ubiquitination - 1mix-TMT. Comparing the global profiling of protein $GSDMD$ with the ubiquitination of the protein at site $K62$. When looking at the summary of the modification and global protein it was clear the conditions follow different trends. Specifically, there appeared to be no change in abundance between Dox1hr and Dox4hr in the modified plot, however there was a large negative change when looking at the unmodified plot. This indicated the modification was confounded with changes in the unmodified protein.}
\label{fig:profile_plots}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\begin{subfigure}[c]{0.5\linewidth}
\includegraphics[width=1\textwidth]{images/ipah_venn_diagramm.png}
\caption{}
\label{fig:data4_venn_diagram}
\end{subfigure}
\begin{subfigure}[c]{0.5\linewidth}
\includegraphics[width=1\textwidth]{images/shig_venn_diagramm.png}
\caption{}
\label{fig:data5_venn_diagram}
\end{subfigure}
\caption{
\todo{Update the figure titles}
%
a) Dataset 4: Human - Ubiquitination - 1mix-TMT. The overlap of differential modified peptides for the PTM model with and without global protein level adjustment across all comparisons.  3,236 modified peptides became insignificant, 1,352 became significant, while 4,282 were significant in both models. b) Dataset 5: Mouse - Phosphorylation - 2mix-TMT. The overlap of differentially modified peptides between the PTM model with and without global protein level adjustment across all comparisons. 19,286 peptides became insignificant, 4,947 became significant, and 41,552 were significant in both models. }
\label{fig:venn_diagrams}
\end{figure}

\begin{figure}[h!]
\centering
\begin{subfigure}{\textwidth}
 \centering
\includegraphics[width=1.0\textwidth]{images/No_Difference_Shigella_Profile_Plot}
\caption{}
\label{fig:data4_profile_plot}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=1.0\textwidth]{images/IpaH_prof_plot.png}
	\caption{}
	\label{fig:data5_profile_plot}
	 \end{subfigure}
\caption{a) Dataset 5: Mouse - Phosphorylation - 2mix-TMT. Comparing the global profiling of protein $TTP$ with the modification at site $S178$. The modification and unmodified protein abundance followed the same trend across conditions. Specifically, there was a positive adjustment in abundance when comparing WT\_Uninfect to WT\_Late in both the modification and global profiling run. b) Dataset 4: Human - Ubiquitination - 1mix-TMT. Comparing the global profiling of protein $GSDMD$ with the ubiquitination of the protein at site $K62$. Here the modification and global protein follow different trends. There appeared to be no change in abundance between Dox1hr and Dox4hr in the modified plot, however there was a large negative change when looking at the unmodified plot. This indicated the modification was confounded with changes in the unmodified protein.}
\label{fig:profile_plots}
\end{figure}
